Nu! the hiding of Hadit.

Come! all ye, and learn the secret that hath not yet been revealed. I, Hadit, am the complement of Nu, my bride. I am not extended, and Khabs is the name of my House.

In the sphere I am everywhere the centre, as she, the circumference, is nowhere found.

Yet she shall be known \& I never.

Behold! the rituals of the old time are black. Let the evil ones be cast away; let the good ones be purged by the prophet! Then shall this Knowledge go aright.

I am the flame that burns in every heart of man, and in the core of every star. I am Life, and the giver of Life, yet therefore is theknowledge of me the knowledge of death.

I am the Magician and the Exorcist. I am the axle of the wheel, and the cube in the circle. "Come unto me" is a foolish word: for it is I that go.

Who worshipped Heru-pa-kraath have worshipped me; ill, for I am the worshipper.

Remember all ye that existence is pure joy; that all the sorrows are but as shadows; they pass \& are done; but there is that which remains.

O prophet! thou hast ill will to learn this writing.

I see thee hate the hand \& the pen; but I am stronger.

Because of me in Thee which thou knewest not.

for why? Because thou wast the knower, and me.

Now let there be a veiling of this shrine: now let the light devour men and eat them up with blindness!

For I am perfect, being Not; and my number is nine by the fools; but with the just I am eight, and one in eight: Which is vital, for I am none indeed. The Empress and the King are not of me; for there is a further secret.

I am The Empress \& the Hierophant. Thus eleven, as my bride is eleven.

Hear me, ye people of sighing!
The sorrows of pain and regret
Are left to the dead and the dying,
The folk that not know me as yet.

These are dead, these fellows; they feel not. We are not for the poor and sad: the lords of the earth are our kinsfolk.

Is a God to live in a dog? No! but the highest are of us. They shall rejoice, our chosen: who sorroweth is not of us.

Beauty and strength, leaping laughter and delicious languor, force and fire, are of us.

We have nothing with the outcast and the unfit: let them die in their misery. For they feel not. Compassion is the vice of kings: stamp down the wretched \& the weak: this is the law of the strong: this is our law and the joy of the world. Think not, o king, upon that lie: That Thou Must Die: verily thou shalt not die, but live. Now let it be understood: If the body of the King dissolve, he shall remain in pure ecstasy for ever. Nuit! Hadit! Ra-Hoor-Khuit! The Sun, Strength \& Sight, Light; these are for the servants of the Star \& the Snake.

I am the Snake that giveth Knowledge \& Delight and bright glory, and stir the hearts of men with drunkenness. To worship me take wine and strange drugs whereof I will tell my prophet, \& be drunk thereof! They shall not harm ye at all. It is a lie, this folly against self. The exposure of innocence is a lie. Be strong, o man! lust, enjoy all things of sense and rapture: fear not that any God shall deny thee for this.

I am alone: there is no God where I am.

Behold! these be grave mysteries; for there are also of my friends who be hermits. Now think not to find them in the forest or on the mountain; but in beds of purple, caressed by magnificent beasts of women with large limbs, and fire and light in their eyes, and masses of flaming hair about them; there shall ye find them. Ye shall see them at rule, at victorious armies, at all the joy; and there shall be in them a joy a million times greater than this. Beware lest any force another, King against King! Love one another with burning hearts; on the low men trample in the fierce lust of your pride, in the day of your wrath.

Ye are against the people, O my chosen!

I am the secret Serpent coiled about to spring: in my coiling there is joy. If I lift up my head, I and my Nuit are one. If I droop down mine head, and shoot forth venom, then is rapture of the earth, and I and the earth are one.

There is great danger in me; for who doth not understand these runes shall make a great miss. He shall fall down into the pit called Because, and there he shall perish with the dogs of Reason.

Now a curse upon Because and his kin!

May Because be accursed for ever!

If Will stops and cries Why, invoking Because, then Will stops \& does nought.

If Power asks why, then is Power weakness.

Also reason is a lie; for there is a factor infinite \& unknown; \& all their words are skew-wise.

Enough of Because! Be he damned for a dog!

But ye, o my people, rise up \& awake!

Let the rituals be rightly performed with joy \& beauty!

There are rituals of the elements and feasts of the times.

A feast for the first night of the Prophet and his Bride!

A feast for the three days of the writing of the Book of the Law.

A feast for Tahuti and the child of the Prophet--secret, O Prophet!

A feast for the Supreme Ritual, and a feast for the Equinox of the Gods.

A feast for fire and a feast for water; a feast for life and a greater feast for death!

A feast every day in your hearts in the joy of my rapture!

A feast every night unto Nu, and the pleasure of uttermost delight!

Aye! feast! rejoice! there is no dread hereafter. There is the dissolution, and eternal ecstasy in the kisses of Nu.

There is death for the dogs.

Dost thou fail? Art thou sorry? Is fear in thine heart?

Where I am these are not.

Pity not the fallen! I never knew them. I am not for them. I console not: I hate the consoled \& the consoler.

I am unique \& conqueror. I am not of the slaves that perish. Be they damned \& dead! Amen. (This is of the 4: there is a fifth who is invisible, \& therein am I as a babe in an egg. )

Blue am I and gold in the light of my bride: but the red gleam is in my eyes; \& my spangles are purple \& green.

Purple beyond purple: it is the light higher than eyesight.

There is a veil: that veil is black. It is the veil of the modest woman; it is the veil of sorrow, \& the pall of death: this is none of me. Tear down that lying spectre of the centuries: veil not your vices in virtuous words: these vices are my service; ye do well, \& I will reward you here and hereafter.

Fear not, o prophet, when these words are said, thou shalt not be sorry. Thou art emphatically my chosen; and blessed are the eyes that thou shalt look upon with gladness. But I will hide thee in a mask of sorrow: they that see thee shall fear thou art fallen: but I lift thee up.

Nor shall they who cry aloud their folly that thou meanest nought avail; thou shall reveal it: thou availest: they are the slaves of because: They are not of me. The stops as thou wilt; the letters? change them not in style or value!

Thou shalt obtain the order \& value of the English Alphabet; thou shalt find new symbols to attribute them unto.

Begone! ye mockers; even though ye laugh in my honour ye shall laugh not long: then when ye are sad know that I have forsaken you.

He that is righteous shall be righteous still; he that is filthy shall be filthy still.

Yea! deem not of change: ye shall be as ye are, \& not other. Therefore the kings of the earth shall be Kings for ever: the slaves shall serve. There is none that shall be cast down or lifted up: all is ever as it was. Yet there are masked ones my servants: it may be that yonder beggar is a King. A King may choose his garment as he will: there is no certain test: but a beggar cannot hide his poverty.

Beware therefore! Love all, lest perchance is a King concealed! Say you so? Fool! If he be a King, thou canst not hurt him.

Therefore strike hard \& low, and to hell with them, master!

There is a light before thine eyes, o prophet, a light undesired, most desirable.

I am uplifted in thine heart; and the kisses of the stars rain hard upon thy body.

Thou art exhaust in the voluptuous fullness of the inspiration; the expiration is sweeter than death, more rapid and laughterful than a caress of Hell's own worm.

Oh! thou art overcome: we are upon thee; our delight is all over thee: hail! hail: prophet of Nu! prophet of Had! prophet of Ra-Hoor-Khu! Now rejoice! now come in our splendour \& rapture! Come in our passionate peace, \& write sweet words for the Kings.

I am the Master: thou art the Holy Chosen One.

Write, \& find ecstasy in writing! Work, \& be our bed in working! Thrill with the joy of life \& death! Ah! thy death shall be lovely: whososeeth it shall be glad. Thy death shall be the seal of the promise of our age long love. Come! lift up thine heart \& rejoice! We are one; we are none.

Hold! Hold! Bear up in thy rapture; fall not in swoon of the excellent kisses!

Harder! Hold up thyself! Lift thine head! breathe not so deep -- die!

Ah! Ah! What do I feel? Is the word exhausted?

There is help \& hope in other spells. Wisdom says: be strong! Then canst thou bear more joy. Be not animal; refine thy rapture! If thou drink, drink by the eight and ninety rules of art: if thou love, exceed by delicacy; and if thou do aught joyous, let there be subtlety therein!

But exceed! exceed!

Strive ever to more! and if thou art truly mine -- and doubt it not, an if thou art ever joyous! -- death is the crown of all.

Ah! Ah! Death! Death! thou shalt long for death. Death is forbidden, o man, unto thee.

The length of thy longing shall be the strength of its glory. He that lives long \& desires death much is ever the King among the Kings.

Aye! listen to the numbers \& the words:

4 6 3 8 A B K 2 4 A L G M O R 3 Y X 24 89 R P S T O V A L. What meaneth this, o prophet? Thou knowest not; nor shalt thou know ever. There cometh one to follow thee: he shall expound it. But remember, o chose none, to be me; to follow the love of Nu in the star-lit heaven; to look forth upon men, to tell them this glad word.

O be thou proud and mighty among men!

Lift up thyself! for there is none like unto thee among men or among Gods! Lift up thyself, o my prophet, thy stature shall surpass the stars. They shall worship thy name, foursquare, mystic, wonderful, the number of the man; and the name of thy house 418.

The end of the hiding of Hadit; and blessing \& worship to the prophet of the lovely Star!
